This PDF is a Git Repository\\Containing its Own \LaTeX\ Source\\and a Copy of Itself

### 2017-05-10 article.tex
Fixed a typo and cleaned up some wording

At this point, we have all the tools necessary to create a generalized
PDF/Git Bundle polyglot for \emph{almost} any PDF and git
repository. The only remaining hurdle is that some viewers require
that the PDF occur as early in the packfile as possible. At first, I
considered applying another patch directly the git source code to make
the uncompressed object first in the packfile. This approach proved to
be very involved, in part due to git's UNIX design philosophy and
architecture of generic code reuse. We're already updating the
packfile's SHA-1 hash due to changing the DEFLATE headers, so instead
I decided to simply reorder the objects after-the-fact, subsequent to
the DEFLATE header fix but before we update the hash. The only
challenge is that moving objects in the packfile has the potential to
break offset delta objects, since they refer to their base objects via
a byte offset within the packfile.  Moving the PDF to the beginning
will break any offset delta objects that occur after the original
position of the PDF that refer to base objects that occur before the
original position of the PDF. That's why I had to dive deeper into the
rabbit hole of the packfile format to understand the delta object
headers (as you saw at the end of Section~\ref{sec:GitBundleFormat},
if you were brave enough to finish it), since I originally attempted
to rewrite the broken ones. Rewriting the broken offset delta objects
is the \emph{correct} solution, but, in the end, I discovered a much
simpler way.

>>>>

At this point, we have all the tools necessary to create a generalized
PDF/Git Bundle polyglot for \emph{almost} any PDF and git
repository. The only remaining hurdle is that some viewers require
that the PDF occur as early in the packfile as possible. At first, I
considered applying another patch directly to the git source code to
make the uncompressed object first in the packfile. This approach
proved to be very involved, in part due to git's UNIX design
philosophy and architecture of generic code reuse. We're already
updating the packfile's SHA-1 hash due to changing the DEFLATE
headers, so instead I decided to simply reorder the objects
after-the-fact, subsequent to the DEFLATE header fix but before we
update the hash. The only challenge is that moving objects in the
packfile has the potential to break offset delta objects, since they
refer to their base objects via a byte offset within the packfile.
Moving the PDF to the beginning will break any offset delta objects
that occur after the original position of the PDF that refer to base
objects that occur before the original position of the PDF. I
originally attempted to rewrite the broken offset delta objects, which
is why I had to dive deeper into the rabbit hole of the packfile
format to understand the delta object headers (as you saw at the end
of Section~\ref{sec:GitBundleFormat}, if you were brave enough to
finish it). Rewriting the broken offset delta objects is
the \emph{correct} solution, but, in the end, I discovered a much
simpler way.
